Case study validations of automatic bullet matching

### 2018-10-24 index.Rmd
Add reference and comment

\begin{table}[ht]
\centering
\begin{tabular}{llrr}
  \hline
\bf study & \bf set & \bf AUC(RF score) & \bf AUC(Cross-correlation) \\ 
  \hline
\bf Hamby 44 &  & 0.956 & 0.926 \\ 
\bf   Phoenix PD &  & 0.976 & 0.986 \\ 
\bf   Houston FSI & G1 & 0.991 & 0.988 \\ 
\bf   Houston FSI & G2 & 0.898 & 0.902 \\ 
\bf   Houston FSI & G3 & 0.986 & 0.987 \\ 
   \hline
\end{tabular}
\caption{Area under the curve (AUC) for each (set) of the studies. As seen in the ROC curves, the algorithm performs the least well on set 2 of the Houston FSI study. Overall the perform on all sets is very good to excellent.
At the land level there is no difference in prediction power between RF score and cross-correlation.\label{tab:aucs}} 
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{llrr}
  \hline
\bf study & \bf set & \bf AUC(RF score) & \bf AUC(Cross-correlation) \\ 
  \hline
\bf Hamby 44 &  & 0.956 & 0.926 \\ 
\bf   Phoenix PD &  & 0.976 & 0.986 \\ 
\bf   Houston FSI & G1 & 0.991 & 0.988 \\ 
\bf   Houston FSI & G2 & 0.898 & 0.902 \\ 
\bf   Houston FSI & G3 & 0.986 & 0.987 \\ 
   \hline
\end{tabular}
\caption{Area under the curve (AUC) for each (set) of the studies. As seen in the ROC curves, the algorithm performs the least well on set 2 of the Houston FSI study. Overall the performance on all sets is very good to excellent.
At the land level there is no difference in prediction power between RF score and cross-correlation. \svp{It has been observed \citep{marzban_roc_2004} that AUC differentiates good models from bad, but does not effectively distinguish between good models to determine which model is better.} \label{tab:aucs}} 
\end{table}
